%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Programming}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}

%------------------------------------------------

\cvskill
{Python} % Category
{
  \begin{cvitems}
  \item {As a general purpose programming language.}
  \item {Experience using Numpy, Pandas and PySpark for data processing.}
  \item {Experience using Scikit-learn and Tensorflow for machine learning.}
  \item {Experience using Flask for backend web development.}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{C} % Category
{
  \begin{cvitems}
  \item {Mainly for optimizing specific tasks in scientific programming.}
  \item {Experience writing Python modules over CPython.}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Rust} % Category
{
  \begin{cvitems}
  \item {For Systems Programming in several contexts.}
  \item {Experience developing basic web applications.}
  \item {Experience writing Python modules over CPython.}
  \item {Done small contributions to Rust related projects like Servo, Cargo and Rust itself.}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Javascript} % Category
{
  \begin{cvitems}
  \item {Some experience using ReactJS for frontend web development.}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Java} % Category
{
  \begin{cvitems}
  \item {As a general purpose programming language.}
  \item {Some experience using Hadoop for data processing.}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Elixir/Erlang} % Category
{
  \begin{cvitems}
  \item {As a general purpose programming language.}
  \item {Some experience using OTP for concurrency.}
  \end{cvitems}
}

%------------------------------------------------

\end{cvskills}
